---
title:  'Coding Challenge #4'
subtitle: 'SWORK 881'
author:
- name: Student -  Mele'ana K. 'Akolo
output: html_document
---

## load libraries
```{r}
library(tidyverse)
library(tidymodels)
library(nnet)
library(MASS)
library(splines)
library(dplyr)
```

## load dataset
```{r}
data.01<- read.csv("Data/LHS_exercise_02102022.csv")
```

#data wrangling

We will be creating new variables: 
`anxiety` = clincally significant symptoms of anxiety; score 3 or more on PHQ-4 items 1 & 2
`depression` = clinically significant symptoms of depression; score of 3 or mroe on PHQ-4 items 3 & 4 
`distress` = continuous PHQ-4 score; higher score indicate greater distress
`distress_type` = multinomial variable: 0- none; 1- anxiety; 2- dep; 3- anxiety & dep
(hint: use `str_c(var1, '', var2)` to concatenate two values by rows)
`distress_cat` = categorizing distress score into min:4 ~ 'low'; 5:8 ~ 'mid'; 8:max ~ 'high'
(hint: use `%in%`)
`age_sd` = standardized `age` variable


```{r}
data.01<- data.01%>%
  mutate(anxiety = case_when(phq4_1 >= 3 ~1,
                             TRUE ~ 0))
data.01<- data.01%>%
  mutate(depression = case_when(phq4_1 >=3 ~1,
                             TRUE ~ 0))
  data.01<- data.01 %>%
    mutate(distress = case_when(phq4_1 >=3 ~1,
                             TRUE ~ 0))
   data.03<- data.01%>%
    mutate(distress_avg = rowMeans(across(phq1_1:phq4_1)),
           distress_avg_rev = 4-distress_avg,
           distress_sum_rev = distress_avg_rev*4)%>%
    dplyr::select(distress_sum_rev, age, sex, education)
   data.02$distress_types= as.factor(data.02$distress_types)
  data.02$distress_types2<- relevel(data.02$distress_types, ref = phq4_1)
  data.02$distress_types2 <- str_c(var0-none, '', var1- anxiety,"",var2- dep,"",var3- anxiety & dep)
  data.02<-data.01 %in%
    dplyr::select (low, mid, high) %in%
    mutate(distress_cat =
             case_when(distress == min:4 ~ low, 5:8 ~ mid, 8:max ~ high))
data.02$age_sd<- scale(data.02$age)

```

Report frequency of `distress_type`
> [ Answer goes here  ].

_hint_: your **none** category must have $n=322$; if you do not have this, check your code again.


Report frequency of `distress_cat`
> [ Answer goes here ].

_hint_: your **mid** category must have $n=170$; if you do not have this, check your code again.

---
## multinomial logistic regression

Run multinomial regression where DV is `distress_type`. Use `anxiety` as your reference category. 
Use your typical list of independent variables (standardized age, sex, education). 
 
_hint_: use `nnet` package's `multinom` function

```{r}
fit.mlr<- multinom(distress_types2, age+ factor(sex) + factor(education),
                   data = data.03)
```

Please note your interpretation unit and your outcome unit must be the same. If needed, trasnform your output to facilitate  your interpretation.

Focusing on those who reported both _anxiety_ **AND** _depression_ as your outcome level of interest, provide your interpretation below:
> [Provide your interpretation here]


---
## ordinal logistic regression

Run ordinal regression where DV is `distress_cat`. Use your typical list of independent variables (standardized age, sex, education).

```{r}


```
To the best of your knowledge, provide explanation of the result. 

> [Provide your description of the result here]


---
## splines!

Run linear regression where DV is `distress`. For your standardized age variable, locate knot points at `-0.5`, `0`, and `0.5`. 

```{r}

```

Provide your interpretation below:
> [Provide your interpretation here]


Run logistic regression where DV is `depression`. For your standardized age variable, locate knot points at  `-1`, `0`, and `1`. 

```{r}

```
Provide your interpretation below:
> [Provide your interpretation here]
